### 2021-05-18 sections/queueing_model/main.tex
Change the way equations are cited
Include brackets around cited equations

We denote the state space of the Markov chain as  \(S=S(T)\) which can be 
written as the disjoint union~\ref{eq:definition_of_S_as_disjoint_union}.

@@

The transition matrix \(Q\) of the Markov chain consists of the transition rates
between the numerous states of the model. Every entry \( Q_{ij} = 
Q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
\( (u_i, v_i), (u_j, v_j) \in S \).
The entries of \(Q\) can be calculated using the state-mapping function 
described in \ref{eq:markov_transition_rate}:

@@

In order to consider this model numerically an adjustment needs 
to be made. 
The problem defined above assumes no upper boundary to the number of individuals 
that can wait for service or for the ones that are blocked in the buffer centre. 
Therefore, a different state space \( \tilde S \) needs to be constructed where 
\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals \(N\) 
that can be in the system and a maximum allowed number of individuals \(M\) that can
be blocked in the buffer centre:

>>>>

We denote the state space of the Markov chain as  \(S=S(T)\) which can be 
written as the disjoint union (\ref{eq:definition_of_S_as_disjoint_union}).

@@

The transition matrix \(Q\) of the Markov chain consists of the transition rates
between the numerous states of the model. Every entry \( Q_{ij} = 
Q_{(u_i, v_i),(u_j, v_j)} \) represents the transition rate from state 
\( i = (u_i, v_i) \) to state \( j = (u_j , v_j) \) for all 
\( (u_i, v_i), (u_j, v_j) \in S \).
The entries of \(Q\) can be calculated using the state-mapping function 
described in (\ref{eq:markov_transition_rate}):

@@

In order to consider this model numerically an adjustment needs to be made. 
The problem defined above assumes no upper boundary to the number of individuals 
that can wait for service or for the ones that are blocked in the buffer centre. 
Therefore, a different state space \( \tilde S \) is constructed where 
\( \tilde S \subseteq S \) and there is a maximum allowed number of individuals 
\(N\) that can be in the system and a maximum allowed number of individuals 
\(M\) that can be blocked in the buffer centre:

### 2021-05-18 sections/queueing_model/subsections/performance_measures/blocking_time/main.tex
Change the way equations are cited
Include brackets around cited equations

In order to not consider individuals that will be lost to the system, the set of 
accepting states needs to be taken into consideration. 
As defined in section \ref{sec:waiting_time}, the set of accepting states is 
given by \ref{eq:accepting_states_class_2}:

@@

In equation \ref{eq:time_in_state_blocking_time}, both service completions and 
class 1 arrivals are considered. 
Thus, from a blocked individual's perspective whenever the system moves from one 
state \((u,v)\)
to another state it can either:

@@

A direct approach will be used to solve this equation here. 
By enumerating all equations of (\ref{eq:general_blocking_time_at_each_state}) 
for all states \((u,v)\) that belong in \(S_b\) 
a system of linear equations arises where the unknown variables are all the 
\(b(u,v)\) terms. 
Note here that these equations correspond to all blocking states as defined in
\ref{eq:set_of_blocking_states}. 
Equations that correspond to non-blocking states have a value of \(0\) as 
defined in \ref{eq:general_blocking_time_at_each_state}
The general form of the equation in terms of \(C,T,N \text{ and } M\) is given by:

@@

The equivalent matrix notation of the linear system of equations 
(\ref{eq:first_eq_of_blocking_general}) - (\ref{eq:last_eq_of_blocking_general})
is given by \(Zx=y\), where:
\begin{equation}\label{eq:general_algebaric_approach_blocking_time}
    \scalebox{0.73}{\(
        Z = 
        \begin{pmatrix}
            -1 & p_o & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T)
            p_s & -1 & p_o & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+1)
            0 & p_s & -1 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+2)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 1 & -1 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,N)
            p_s & 0 & 0 & \dots & 0 & 0 & -1 & p_o & 0 & \dots & 0 & 0 \\ %(2,T)
            0 & 0 & 0 & \dots & 0 & 0 & p_s & -1 & p_o & \dots & 0 & 0 \\ %(2,T+1)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 1 & -1 \\ %(M,N)
        \end{pmatrix},
        x = 
        \begin{pmatrix}
            b(1,T) \\
            b(1,T+1) \\
            b(1,T+2) \\
            \vdots \\
            b(1,N) \\
            b(2,T) \\
            b(2,T+1) \\
            \vdots \\
            b(M,N) \\
        \end{pmatrix}, 
        y= 
        \begin{pmatrix}
            -c(1,T) \\
            -c(1,T+1) \\
            -c(1,T+2) \\
            \vdots \\
            -c(1,N) \\
            -c(2,T) \\
            -c(2,T+1) \\
            \vdots \\
            -c(M,N) \\
        \end{pmatrix}
    \)}
\end{equation}

@@

To illustrate how the described formula works consider a Markov model where 
\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example_algeb_blocking}). 
The equations that correspond to such a model are shown in 
(\ref{eq:first_eq_of_blocking_example})-(\ref{eq:last_eq_of_blocking_example}) 
and their equivalent matrix notation form is shown in 
\ref{eq:example_algebaric_approach_blocking_time}.

>>>>

In order to not consider individuals that will be lost to the system, the set of 
accepting states needs to be taken into consideration. 
As defined in section \ref{sec:waiting_time}, the set of accepting states is 
given by (\ref{eq:accepting_states_class_2}):

@@

In equation (\ref{eq:time_in_state_blocking_time}), both service completions and 
class 1 arrivals are considered. 
Thus, from a blocked individual's perspective whenever the system moves from one 
state \((u,v)\)
to another state it can either:

@@

A direct approach will be used to solve this equation here. 
By enumerating all equations of ((\ref{eq:general_blocking_time_at_each_state})) 
for all states \((u,v)\) that belong in \(S_b\) 
a system of linear equations arises where the unknown variables are all the 
\(b(u,v)\) terms. 
Note here that these equations correspond to all blocking states as defined in
(\ref{eq:set_of_blocking_states}). 
Equations that correspond to non-blocking states have a value of \(0\) as 
defined in (\ref{eq:general_blocking_time_at_each_state})
The general form of the equation in terms of \(C,T,N \text{ and } M\) is given by:

@@

The equivalent matrix notation of the linear system of equations 
((\ref{eq:first_eq_of_blocking_general})) - ((\ref{eq:last_eq_of_blocking_general}))
is given by \(Zx=y\), where:
\begin{equation}\label{eq:general_algebaric_approach_blocking_time}
    \scalebox{0.73}{\(
        Z = 
        \begin{pmatrix}
            -1 & p_o & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T)
            p_s & -1 & p_o & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+1)
            0 & p_s & -1 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,T+2)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 1 & -1 & 0 & 0 & 0 & \dots & 0 & 0 \\ %(1,N)
            p_s & 0 & 0 & \dots & 0 & 0 & -1 & p_o & 0 & \dots & 0 & 0 \\ %(2,T)
            0 & 0 & 0 & \dots & 0 & 0 & p_s & -1 & p_o & \dots & 0 & 0 \\ %(2,T+1)
            \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & 
            \vdots & \vdots & \ddots & \vdots & \vdots \\ 
            0 & 0 & 0 & \dots & 0 & 0 & 0 & 0 & 0 & \dots & 1 & -1 \\ %(M,N)
        \end{pmatrix},
        x = 
        \begin{pmatrix}
            b(1,T) \\
            b(1,T+1) \\
            b(1,T+2) \\
            \vdots \\
            b(1,N) \\
            b(2,T) \\
            b(2,T+1) \\
            \vdots \\
            b(M,N) \\
        \end{pmatrix}, 
        y= 
        \begin{pmatrix}
            -c(1,T) \\
            -c(1,T+1) \\
            -c(1,T+2) \\
            \vdots \\
            -c(1,N) \\
            -c(2,T) \\
            -c(2,T+1) \\
            \vdots \\
            -c(M,N) \\
        \end{pmatrix}
    \)}
\end{equation}

@@

To illustrate how the described formula works consider a Markov model where 
\(C=2, T=2, N=4, M=2\) (figure \ref{fig:example_algeb_blocking}). 
The equations that correspond to such a model are shown in 
((\ref{eq:first_eq_of_blocking_example}))-((\ref{eq:last_eq_of_blocking_example})) 
and their equivalent matrix notation form is shown in 
(\ref{eq:example_algebaric_approach_blocking_time}).

### 2021-05-18 sections/queueing_model/subsections/performance_measures/main.tex
Change the way equations are cited
Include brackets around cited equations

The transition matrix \( Q \) defined in \ref{eq:markov_transition_rate} can be 
used to get the probability vector \( \pi \).
The vector \( \pi \) is commonly used to study stochastic systems and it's main
purpose is to keep track of the probability of being at any given state of 
the system. \(\pi_i\) is the steady state probability of being in state \((u_i, v_i)\in\tilde S\) which is the \(i\)th state of \(tilde S\) for some ordering of \(\tilde S\).
The term \textit{steady state} refers to the instance of the vector \( \pi \) 
where the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \( Q \) is given by:

>>>>

The transition matrix \( Q \) defined in (\ref{eq:markov_transition_rate}) can 
be used to get the probability vector \( \pi \).
The vector \( \pi \) is commonly used to study stochastic systems and it's main
purpose is to keep track of the probability of being at any given state of 
the system. 
\(\pi_i\) is the steady state probability of being in state \((u_i, v_i) \in 
\tilde S\) which is the \(i^{\text{th}}\) state of \(\tilde S\) for some ordering of 
\(\tilde S\).
The term \textit{steady state} refers to the instance of the vector \( \pi \) 
where the probabilities of being at any state become stable over time. 
Thus, by considering the steady state vector \( \pi \) the relationship between 
it and \( Q \) is given by:

### 2021-05-18 sections/queueing_model/subsections/performance_measures/waiting_time/main.tex
Change the way equations are cited
Include brackets around cited equations

Note here that if the threshold is less than or equal the total capacity of the
system the set includes all states that are not on the last column of the 
Markov chain.
Otherwise, the set of accepting state is identical to 
\ref{eq:accepting_states_class_1}. Thus, the expressions for the waiting times 
for class 1 and class 2 individuals are given by:

@@

The two coefficients represent the proportion of individuals of each type that 
did not get lost and traversed through the model.
Thus, one should account for the probability that an individual is lost to the 
system. 
This probability can be easily calculated by using the two sets of accepting 
states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
\ref{eq:accepting_states_class_1} and \ref{eq:accepting_states_class_2}. 
Using these equations the probability, for either class type, that an individual 
is not lost in the system is given by:

@@

Thus, by using these values as the coefficient of equation 
\ref{eq:overall_waiting_time_coeff} the resultant equation can be used to get 
the overall waiting time.

>>>>

Note here that if the threshold is less than or equal the total capacity of the
system the set includes all states that are not on the last column of the 
Markov chain.
Otherwise, the set of accepting state is identical to 
(\ref{eq:accepting_states_class_1}). Thus, the expressions for the waiting times 
for class 1 and class 2 individuals are given by:

@@

The two coefficients represent the proportion of individuals of each type that 
did not get lost and traversed through the model.
Thus, one should account for the probability that an individual is lost to the 
system. 
This probability can be easily calculated by using the two sets of accepting 
states \(S_A^{(2)}\) and \(S_A^{(1)}\) defined in equations 
(\ref{eq:accepting_states_class_1}) and (\ref{eq:accepting_states_class_2}). 
Using these equations the probability, for either class type, that an individual 
is not lost in the system is given by:

@@

Thus, by using these values as the coefficient of equation 
(\ref{eq:overall_waiting_time_coeff}) the resultant equation can be used to get 
the overall waiting time.
